\documentclass[12pt]{article} 
 	
 	\usepackage{float} 
 	\usepackage{geometry} 
 	\usepackage{fancyhdr} 
 	\usepackage{longtable} 
 	\usepackage{placeins} 
 	\usepackage{enumitem} 
 	
 	% times new roman font 
 	\usepackage[T1]{fontenc} 
 	\usepackage[utf8]{inputenc} 
 	\usepackage{mathptmx} 
 	
 	\pagestyle{fancy} 
 	\geometry{margin=0.5in} 
 	\setlength{\parindent}{30pt} 
 	
 	\title{TREK \\ Packing List} 
 	
 	\begin{document} 
 	
 	\maketitle 
 	
 	\iffalse 
 	\fi 
 	
 	\noindent 
 	\section{Packing List Items} 
 	\FloatBarrier 
 	\begin{longtable}{|p{1.5in}|p{0.75in}|p{4.75in}|} \hline 
 		\textbf{Item} & \textbf{Quantity} & \textbf{Notes about Item} \ \hline  
360 degree visible white deck light & 1 &  \ \hline 
air mattress & 1 &  \ \hline 
air mattress repair kit & 1 & You're not a thin as you think. \ \hline 
aqua tabs & 12 & Follow directions on packaging. \ \hline 
backpack & 1 & Backpacks are rated in Litres, for the volume of gear they hold. \ \hline 
bailing bucket & 1 &  \ \hline 
biodegradeable camp soap & 1 & Camp soap is only biodegradeable on land. Do not use directly in a body of water. Read the label. \ \hline 
boots & 1 & High-cut, lots of toe room. \ \hline 
bowls, plates, utensils & 1 & Small plastic utensils are more appropriate for hiking than metal ones. \ \hline 
bug spray & 1 & Higher the deet content, the more effective it is. Warning: bugspray is inneffective against the rodent-size mosquitoes of the French River. \ \hline 
coleman stove & 1 & Some stoves have flaps to prevent wind from redirecting the flame. \ \hline 
compass & 1 &  \ \hline 
deck compass & 1 &  \ \hline 
dry bags & 3 & Make sure to roll them at least 3 times before closing. Make sure to keep enough air inside of the bag so that the whole bag will float. \ \hline 
dry-fit shirt & 2 &  \ \hline 
dry-fit shorts & 2 &  \ \hline 
emergency warmth blanket and kit & 1 & Warmth blanket (made of foil), flares, whistle. \ \hline 
extra socks & 2 &  \ \hline 
first aid kit & 1 & Waterproof band-aids, disinfectant, polysporin, scissors. \ \hline 
flares & 1 &  \ \hline 
flashlight & 2 & A waterproof flashlight is a good idea. \ \hline 
floating rope 50ft & 1 &  \ \hline 
food barrel & 1 &  \ \hline 
garbage bags (make sure they are resealable) & 10 & Resealable bags are a good idea. Bring many garbage bags because you end up using them for other purposes, like waterproofing things. \ \hline 
general purpose knife & 1 &  \ \hline 
ground cover & 1 & Put a ground cover under the tent to prevent condensation from the ground. \ \hline 
hiking pants & 1 & Pants while hiking prevents ticks from biting you and giving you Lyme Disease \ \hline 
kayak & 1 &  \ \hline 
kayak paddle & 1 &  \ \hline 
kayak radar reflector & 1 &  \ \hline 
kayak repair kit (adhesive, plastic patches, marine epoxy) & 1 &  \ \hline 
kayaking map & 1 &  \ \hline 
life jacket or PFD & 1 &  \ \hline 
lighter & 2 & Make sure it is refilled before a trip. "Windproof" lighters (aka. torch lighters) have a blue jet flame that burns hotter than red \ \hline 
map & 1 &  \ \hline 
marine radio & 1 &  \ \hline 
marine radio frequency channels chart & 1 &  \ \hline 
passive sound-signalling device. ex. whistle & 1 &  \ \hline 
pillow & 1 &  \ \hline 
polarizing sun glasses & 1 & Polarized lenses cut down on glare, so you can see fish underwater better. \ \hline 
pots and pans & 1 &  \ \hline 
rain jacket and pants & 1 &  \ \hline 
rope & 2 & Use two different rope materials, one slippery to the touch, the other one rough. This helps you make different kinds of knots. \ \hline 
saw or hatchet & 1 &  \ \hline 
sleeping bag & 1 &  \ \hline 
sleeping pad & 1 & Inflatable pads compensate for uneven terrian better than foam pads, and are more compact. \ \hline 
sunscreen & 1 & Higher SPF is more protection, but is it also more cancer? \ \hline 
tarp & 1 & Bring bungee cords and make sure the tarp does not touch any part of the tent because in the morning condensation forms and may leak into the tent. Useful Knots: bowline \ \hline 
tent & 1 & Useful knots: bowline (connect the top of the tent to a tree), alpine loop (shorten a rope), blood loop (adding extra loops to the line for hanging things from a caribiner) \ \hline 
tidal and wave charts & 1 &  \ \hline 
toiletries (tooth paste, tooth brush, floss, nail clippers, toilet paper) & 1 & Tooth brush, tooth paste, floss, nail clippers (you may chip it during a fall) \ \hline 
tylenol & 10 &  \ \hline 
wateproof flashlight & 1 &  \ \hline 
water bottle & 1 & Choose a hard-shell water bottle: it can be used for different purposess, including a container for something fragile. \ \hline 
water shoes & 1 &  \ \hline 
 	\end{longtable} 
 	\FloatBarrier 
 	 
 	\section{General Notes} 
 	\begin{enumerate}[itemsep=-1ex] 
 		\item Affirmer offers the Work as-is and makes no representations or 
 		warranties of any kind concerning the Work, express, implied, 
 		statutory or otherwise, including without limitation warranties of 
 		title, merchantability, fitness for a particular purpose, non 
 		infringement, or the absence of latent or other defects, accuracy, or 
 		the present or absence of errors, whether or not discoverable, all to 
 		the greatest extent permissible under applicable law. 
 \item Cover up skin and watch out for ticks! \ \hline 
 	\end{enumerate} 
 	
 
	\end{document} 
 